Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-06-18 ICML-camera-ready/main-all.tex
acknowledgement

\bibliography{biblio}
\bibliographystyle{icml2019}

% For actual submission remove everything below.
% Use appendices only in supplementray material.
\appendix
\clearpage

>>>>

\section*{Acknowledgments} We thank Francesco Orabona and Wen Sun
for helpful initial discussions, and thank Adam Klivans and Rocco \mbox{Servedio} for helpful
discussions on~\citep{Klivans-Servedio-2008} and
pointing out the reference~\citep{Klivans-Servedio-2004}. We also thank Dylan Foster, 
Akshay \mbox{Krishnamurthy}, and Haipeng Luo for providing a candidate solution to our problem. 
Finally, we thank Shang-En Huang and \mbox{Mengxiao} Zhang for helpful discussions on the hardness results.

\bibliography{biblio}
%\bibliographystyle{plainnat}
\bibliographystyle{icml2019}

% For actual submission remove everything below.
% Use appendices only in supplementray material.
\onecolumn
\appendix
\clearpage
